Data tests

### 2022-07-28 Old/Shiny/Test/Data tests.Rmd
Actually writing the function.
setequal() testing.

clean_names(blank)
```

@@

```{r}
# This may be the function =====================================================
```

>>>>

clean_names(blank)

getwd()
excel_logic <- read_excel("Data/OPXfinans_final.xlsx") |> clean_names()

excel_logic

excel_names <- names(excel_logic)

excel_names == c("year", "firm", "category", "sub_category", "name", "value")

class(excel_names)

if (excel_names == c("year", "firm", "category", "sub_category", "name", "value")) {
  "yes"
} else {
  "no"
}

setequal(excel_names, c("year", "firm", "category", "sub_category", "name", "value"))
```

@@

```{r}
# This may be the function =====================================================

  if (as.character(all_of(start)) %in% names(htmlready) &&
    as.character(all_of(end)) %in% names(htmlready)) {
    read_proff_notest(file, start, end)
  } else {
    "year error"
  }
}
```
